A new tidy data structure to support exploration and modeling of temporal data

### 2019-11-10 reviews/response.Rmd

---
title: Response to reviewers
author: JCGS-19-044.R1
output:
  MonashEBSTemplates::memo:
    includes:
      in_header: preamble2.tex
fontfamily: mathpazo
---

We thank the Editor, Associate editor and reviewers for their comments which have improved this paper. The point by point description of changes are below: the reviewers' comments are in red and our response is in black.

@@

> P6 L34. Second item missing full stop at the end.

Done.

> I think for Figure 4, you should mention that supplementary figure contains the gif if the animation does not work or perhaps include a link to a working animation.

Thanks. We added a sentence in Figure 4 caption "The animations are available with the supplementary materials online, and can also be viewed directly at <https://github.com/earowang/paper-tsibble/blob/master/img/animate-1.gif>."

### 2019-11-10 cover-letter/cover-letter.Rmd
done with minor revisions

We have undertaken major revision on our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data," based on reviewers' comments.

We have rewritten Section 3 "Contextual semantics" and Section 4 "Temporal data pipelines". Now Section 3 gives a definition of tsibble in relation to tidy data. Section 4 describes a big picture about each module with the focus of temporal data instead of time series before.

A detailed response letter to reviewers has been provided.

We believe that this manuscript has been significantly improved, that is a good fit for the Journal of Computational and Graphical Statistics.

>>>>

We have addressed minor issues that the referees have pointed out on our manuscript titled, "A new tidy data structure to support exploration and modeling of temporal data,".

Two zip files are attached with this submission:

### 2019-11-10 tsibble.Rmd
reveals
done with minor revisions

---
title: "A new tidy data structure to support exploration and modeling of temporal data"
author:
  - familyname: Wang
    othernames: Earo
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : earo.wang@monash.edu
    correspondingauthor: true
  - familyname: Cook
    othernames: Dianne
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : dicook@monash.edu
  - familyname: Hyndman
    othernames: Rob J
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : rob.hyndman@monash.edu
abstract: 'Mining temporal data for information is often inhibited by a multitude of formats: regular or irregular time intervals, point events that need aggregating, multiple observational units or repeated measurements on multiple individuals, and heterogeneous data types.  This work presents a cohesive and conceptual framework for organizing and manipulating temporal data, which in turn flows into visualization, modeling and forecasting routines. Tidy data principles are extended to temporal data by: (1) mapping the semantics of a dataset into its physical layout; (2) including an explicitly declared "index" variable representing time; (3) incorporating a "key" comprising single or multiple variables to uniquely identify units over time. This tidy data representation most naturally supports thinking of operations on the data as building blocks, forming part of a "data pipeline" in time-based contexts. A sound data pipeline facilitates a fluent workflow for analyzing temporal data. The infrastructure of tidy temporal data has been implemented in the R package, called **tsibble**.'
keywords: "time series, longitudinal data, data wrangling, tidy data, R, forecasting, data science, exploratory data analysis, data pipelines"
wpnumber: 12/19
jelcodes: C88, C81, C82, C22, C32
blind: false
cover: false
toc: false
bibliography: [references.bib]
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    dev: "pdf"
---

@@

Inspired by a "primary key" [@codd_relational_1970], a unique identifier for each observation in a relational database, the tsibble key also uniquely identifies each observational unit over time. When constructing a tsibble, any duplicates of key-index (i.e. key-value) pairs will fail, because duplicates signal a data quality issue, which would likely affect subsequent analyses and hence decision making. For example, either `gender` or `country` alone is not enough to be the key for the tuberculosis data. Analysts are encouraged to better understand the data, or reason about the process of data cleaning when handling duplicates. Figure \@ref(fig:tsibble-tidy) demonstrates the tidy module with clear routes required for a tsibble. The rigidity of tsibble, as the fundamental data infrastructure, ensures the validity of subsequent temporal data analysis.

@@

(ref:animate-cap) An illustration of a window of size 5 to compute rolling averages over annual tuberculosis cases in Australia using sliding, tiling and stretching. The animations are available with the supplementary materials online, and can be viewed at <https://github.com/earowang/paper-tsibble/blob/master/img/animate-1.gif>.

>>>>

---
title: "A new tidy data structure to support exploration and modeling of temporal data"
author:
  - familyname: Wang
    othernames: Earo
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia. \newline \newline CSIRO Data61, \newline Private Bag 10, South Clayton, VIC 3169
    email : earo.wang@monash.edu
    correspondingauthor: true
  - familyname: Cook
    othernames: Dianne
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : dicook@monash.edu
  - familyname: Hyndman
    othernames: Rob J
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : rob.hyndman@monash.edu
abstract: 'Mining temporal data for information is often inhibited by a multitude of formats: regular or irregular time intervals, point events that need aggregating, multiple observational units or repeated measurements on multiple individuals, and heterogeneous data types.  This work presents a cohesive and conceptual framework for organizing and manipulating temporal data, which in turn flows into visualization, modeling and forecasting routines. Tidy data principles are extended to temporal data by: (1) mapping the semantics of a dataset into its physical layout; (2) including an explicitly declared "index" variable representing time; (3) incorporating a "key" comprising single or multiple variables to uniquely identify units over time. This tidy data representation most naturally supports thinking of operations on the data as building blocks, forming part of a "data pipeline" in time-based contexts. A sound data pipeline facilitates a fluent workflow for analyzing temporal data. The infrastructure of tidy temporal data has been implemented in the R package, called **tsibble**.'
keywords: "time series, longitudinal data, data wrangling, tidy data, R, forecasting, data science, exploratory data analysis, data pipelines"
wpnumber: 12/19
jelcodes: C88, C81, C82, C22, C32
blind: false
cover: false
toc: false
bibliography: [references.bib]
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    dev: "pdf"
---

@@

Inspired by a "primary key" [@codd_relational_1970], a unique identifier for each observation in a relational database, the tsibble key also uniquely identifies each observational unit over time. When constructing a tsibble, any duplicates of key-index (i.e. key-value) pairs will fail, because duplicates signal a data quality issue, which would likely affect subsequent analyses and hence decision making. For example, either `gender` or `country` alone is not enough to be the key for the tuberculosis data. Analysts are encouraged to better understand the data, or reason about the process of data cleaning when handling duplicates. Figure \@ref(fig:tsibble-tidy) reveals the tidy module with clear routes required for a tsibble. The rigidity of tsibble, as the fundamental data infrastructure, ensures the validity of subsequent temporal data analysis.

@@

(ref:animate-cap) An illustration of a window of size 5 to compute rolling averages over annual tuberculosis cases in Australia using sliding, tiling and stretching. The animations are available with the supplementary materials online, and can also be viewed directly at <https://github.com/earowang/paper-tsibble/blob/master/img/animate-1.gif>.
